abxD01 Paper

### 2015-03-04 PAPER.Rmd
Fix code/section for supplemental figure1

![**Supplemental Figure 1.**](supplemental/FigS1_topdose_inverseSimp.pdf)

@@

> Files saved as "topdose2_tx1_sorted_10x20.pdf" and "topdose2_tx2_sorted_10x20.pdf".
> 
> ### Supplemental Figure 1: correlation plot of diversity with *C. difficile*
> 
> For the correlation calculations see the next section of the results.
> Figure making:
>

@@

#Plot observed vs predicted
#information for plotting
color<-rainbow(7)
colors <- c(control = "black",
          cipro = color[1],
          clinda = "#FFCC00",
          vanc.625 = "#00CC00",
          vanc.3 = "#00CC00",
          vanc.1 = "#00CC00",
          strep5 = "#33FFFF",
          strep.5 = "#33FFFF",
          strep.1 = "#33FFFF",
          cef.5 = color[5],
          cef.3 = color[5],
          cef.1 = color[5],
          amp.5 = color[6],
          amp.5d = color[6],
          metro1 = color[7],
          metro1d = color[7])

>>>>

![**Supplemental Figure 1.**](supplemental/sfigure1.png)

@@

> Files saved as "topdose2_tx1_sorted_10x20.pdf" and "topdose2_tx2_sorted_10x20.pdf".
> 
> ### Supplemental Figure 1: correlation plot of diversity with *C. difficile*
> 
> For the correlation calculations see the next section of the results.
> Figure making:

```
# In mothur:
summary.single(calc=invsimpson-shannon, shared=abxD01.final.an.unique_list.shared, subsample=1625)

```
> Using these results, I selected the samples within the original antibiotic set.  Then I calculated the spearman correlation of *C. difficile* CFU/g feces on day 1 with the level of diversity found in the community on day 0 (day of challenge). Both inverse simpson and shannon indices were included.

diversity<-read.csv("~/Documents/Github/abxD01/supplemental/topdose_diversity.csv",  header=T)
diversity$nextDayCFU <- log((diversity$nextDayCFU+1), 10)

#correlation of top dose
pval.spear <- c()
cor.spear <- c()
count <- 1
for(i in 4:5){
  cor.spear[count] <- cor.test(diversity[,3],diversity[,i], method="spearman")$estimate
  pval.spear[count] <- cor.test(diversity[,3],diversity[,i], method="spearman")$p.value
  count <- count + 1 
}
corr.results <- as.matrix(cbind(cor.spear, pval.spear))
rownames(corr.results) <- names(diversity)[4:5]

# Plot inverse simpson vs. C. difficile levels
color<-rainbow(7)
colors.top <- c(control = "black",
          cipro = color[1],
          clinda = "#FFCC00",
          vanc.625 = "#00CC00",
          strep5 = "#33FFFF",
          cef.5 = color[5],
          amp.5 = "#6600FF",
          metro1 = color[7])

# shapes
pch.top <- c(control = 1,
         cipro = 16,
         clinda = 16,
         vanc.625 = 16,
         strep5 = 16,
         cef.5 = 16,
         amp.5 = 16,
         metro1 = 16)

#these are needed for the legend
legend.labels.top <- c(control = "Control",
            cipro = "Ciprofloxacin",
            clinda = "Clindamycin",
            vanc.625 = "Vancomycin",
            strep5 = "Streptomycin",
            cef.5 = "Cefoperazone",
            amp.5 = "Ampicillin",
            metro1 = "Metronidazole")

par(mar=c(5, 5, 1, 1) +0.1, mgp=c(3, 1, 0)) 
par(mfrow=c(1,1))

plot(diversity$invsimpson[diversity$expgroup=="control"], 
     diversity$nextDayCFU[diversity$expgroup=="control"], 
     pch=pch.top[1], col=colors.top[1], xlim=c(0, 20), ylim=c(0,10),  
     cex=1.5, yaxt="n",  xaxt="n", cex.lab=1,
     ylab=as.expression("Log " ~ italic("C. difficile") ~ " CFU/g feces"), xlab="Inverse Simpson Index")

axis(1, las=1, cex.axis=1, at=seq(0,20, by=2))
axis(2, las=1, cex.axis=1, at=seq(0,10, by=1))

for(i in 2:(length(unique(diversity$expgroup)))){
  points(diversity$invsimpson[diversity$expgroup==names(legend.labels.top)[i]],
         diversity$nextDayCFU[diversity$expgroup==names(legend.labels.top)[i]], 
         pch=pch.top[i], col=colors.top[i], cex=1.5)
}

legend(16, 6, legend=legend.labels.top, pch=pch.top, col=colors.top,  pt.cex=1.5, cex=1, bty="n", y.intersp=1.5)

@@

#Plot observed vs predicted
#information for plotting
color<-rainbow(7)
colors <- c(control = "black",
          cipro = color[1],
          clinda = "#FFCC00",
          vanc.625 = "#00CC00",
          vanc.3 = "#00CC00",
          vanc.1 = "#00CC00",
          strep5 = "#33FFFF",
          strep.5 = "#33FFFF",
          strep.1 = "#33FFFF",
          cef.5 = color[5],
          cef.3 = color[5],
          cef.1 = color[5],
          amp.5 = "#6600FF",
          amp.5d = "#6600FF",
          metro1 = color[7],
          metro1d = color[7])
